### 2018-03-21 Docs/runtime_parameters/runtime_parameters.tex
Clarify description of drdxfac parameter.

\verb= bcx_hi = &  $+x$ boundary condition (valid values are listed in {\tt  boxlib/bc.f90}) & SLIP\_WALL \\

@@

\verb= drdxfac = &  ratio of radial base state zones to Cartesian full state zones for spherical geometry & 1 \\

@@

\verb= beta_type = &  what type of coefficient to use inside the velocity divergence constraint. \newline {\tt beta\_type} = 1 uses $\beta_0$; \newline {\tt beta\_type} = 2 uses $\rho_0$ (anelastic); \newline {\tt beta\_type} = 3 uses 1 (small-scale combustion). & 1 \\

@@

\verb= use_linear_grav_in_beta = &  how to represent gravity in the $\beta_0$ integration: .true. = piecewise linear .false. = piecewise constant & .false. \\

>>>>

\verb= bcx_hi = &  $+x$ boundary condition (valid values are listed in {\tt  amrex/Src/F\_BaseLib/bc.f90}) & SLIP\_WALL \\

@@

\verb= drdxfac = &  Number of radial base state zones per Cartesian full state zone along the first dimension at the finest level for spherical geometry & 1 \\

@@

\verb= beta0_type = &  what type of coefficient to use inside the velocity divergence constraint. \newline {\tt beta\_type} = 1 uses $\beta_0$; \newline {\tt beta\_type} = 2 uses $\rho_0$ (anelastic); \newline {\tt beta\_type} = 3 uses 1 (small-scale combustion). & 1 \\

@@

\verb= use_linear_grav_in_beta0 = &  how to represent gravity in the $\beta_0$ integration: .true. = piecewise linear .false. = piecewise constant & .false. \\
